---
title: "Exploration"
author: "Cyrus Cravens"
date: "Due: 21 FEB 23 at 12:00"
output:
  html_document:
  latex_engine: xelatex
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T)

library(tidyverse)  # Load core packages: 
                    # ggplot2,   for data visualization.
                    # dplyr,     for data manipulation.
                    # tidyr,     for data tidying.
                    # purrr,     for functional programming.
                    # tibble,    for tibbles, a modern re-imagining of data frames.
                    # stringr,   for strings.
                    # forcats,   for factors.
                    # lubridate, for date/times.
                    # readr,     for reading .csv, .tsv, and .fwf files.
                    # readxl,    for reading .xls, and .xlxs files.
                    # feather,   for sharing with Python and other languages.
                    # haven,     for SPSS, SAS and Stata files.
                    # httr,      for web apis.
                    # jsonlite   for JSON.
                    # rvest,     for web scraping.
                    # xml2,      for XML.
                    # modelr,    for modelling within a pipeline
                    # broom,     for turning models into tidy data
                    # hms,       for times.

library(magrittr)   # Pipeline operator
library(lobstr)     # Visualizing abstract syntax trees, stack trees, and object sizes
library(pander)     # Exporting/converting complex pandoc documents, EX: df to Pandoc table
library(ggforce)    # More plot functions on top of ggplot2
library(ggpubr)     # Automatically add p-values and significance levels  plots.
                    # Arrange and annotate multiple plots on the same page. 
                    # Change graphical parameters such as colors and labels.
library(sf)         # Geo-spatial vector manipulation: points, lines, polygons
library(kableExtra) # Generate 90 % of complex/advanced/self-customized/beautiful tables
library(latex2exp)  # Latex axis titles in ggplot2
library(ellipse)    # Simultaneous confidence interval region to check C.I. of 2 slope parameters
library(plotly)     # User interactive plots

library(ellipse)    # Simultaneous confidence interval region to check C.I. of 2 regressors
library(olsrr)      # Model selections
library(leaps)      # Regression subsetting
library(pls)        # Partial Least squares
library(MASS)       # LDA, QDA, OLS, Ridge Regression, Box-Cox, stepAIC, etc,.
library(stats)      # functions for statistical calculations and random number generation.
library(corrplot)   # 	Visualization of a Correlation Matrix
library(class)      # Various functions for classification
library(classifly)  # Explore Classification Models in High Dimensions
library(classmap)   # Visualizing Classification Results
library(knitr)

knitr::opts_chunk$set(error = TRUE)

set.seed(1)        # make random results reproducible

current_dir <- getwd()

if (!is.null(current_dir)) {
  setwd(current_dir)
  remove(current_dir)
}
```

```{r}
snails <- read_csv("Snail2.csv")
snails
```

```{r}
colSums(is.na(snails))
```

**NOTE:** There is are no `NA` values

```{r}
unique(snails$ShellType)
```

**NOTE:** There is a categorical variable with records that are either `Type1` or `Type2`.

```{r}
snails %>% 
  group_by(ShellType) %>% 
  count(ShellType) %>% 
  rename(Totals = n)
```
**NOTE:** There are significantly more `Type2` than `Type1` shells. This could potentially cause the data to be biased towards `Type2` shell types.

```{r}
summary(snails)
```

**NOTE:** `Length` values range from 9.63 to 18.39, Q1 = 12.88 $\mu$ = 13.94, Median = 13.79, Q3 = 14.96

```{r}
snails1 <- snails %>% filter(ShellType == "Type1")
summary(snails1)
```

```{r}
snails2 <- snails %>% filter(ShellType == "Type2")
summary(snails2)
```

**NOTE:** `snail2` MIN and MAX for the `Length` variable are closer to the mean and median, which might suggest less outliers. 

```{r}
# Finding the standard deviation for the snails Length variable 
sd(snails$Length)

# Finding the standard deviation for the snails1 Length variable 
sd(snails1$Length)

# Finding the standard deviation for the snails2 Length variable 
sd(snails2$Length)
```

```{r}
# Finding the standard deviation for the snails Length variable 
var(snails$Length)

# Finding the standard deviation for the snails1 Length variable 
var(snails1$Length)

# Finding the standard deviation for the snails2 Length variable 
var(snails2$Length)
```

**NOTE:** $\sigma^{2}$ for `snail2` `Length` variable are smaller. 

```{r}
ggplot(snails) + 
  geom_point(aes(x=1:nrow(snails), y=Length, colour = ShellType))
```

```{r}
ggplot(snails1) + 
  geom_point(aes(x=1:nrow(snails1), y=Length, colour = ShellType))
```

```{r}
ggplot(snails2) + 
  geom_point(aes(x=1:nrow(snails2), y=Length))
```

**OBSERVATIONS: ** It might be beneficial to break the 

```{r}
pairs(snails[,-1])
```

```{r}
corrplot(cor(snails[,-1]), method="square")
```

```{r}
boxplot(snails[,-1])
```

```{r}
snails_new <- snails %>% 
  mutate(Type = ifelse(ShellType == "Type1", 1 , 2)) %>% 
  relocate(Type, .after = ShellType)
snails_new
```

```{r}
pairs(snails_new[,-1])
```

```{r}
corrplot(cor(snails_new[,-1]), method="square")
```

```{r}
boxplot(snails_new[,-1])
```

```{r}
view(snails)
```

### Question c)
```{r}
lmod_1 <- lm(Length ~ ShellType, snails)
lmod_2 <- lm(Length ~ Width, snails)
lmod_3 <- lm(Length ~ AperHt, snails)
lmod_4 <- lm(Length ~ AperWdt, snails)
lmod_5 <- lm(Length ~ LU, snails)
lmod_6 <- lm(Length ~ LipWdt, snails)
lmod_7 <- lm(Length ~ Type, snails_new)
```

```{r}
summary(lmod_1)
```
```{r}
plot(lmod_1)
```

```{r}
summary(lmod_2)
```
```{r}
plot(lmod_2)
```

```{r}
summary(lmod_3)
```

```{r}
plot(lmod_3)
```

```{r}
summary(lmod_4)
```
```{r}
plot(lmod_4)
```

```{r}
summary(lmod_5)
```
```{r}
plot(lmod_5)
```

```{r}
summary(lmod_6)
```
```{r}
plot(lmod_6)
```
```{r}
summary(lmod_7)
```

```{r}
plot(lmod_7)
```

### Question d)

```{r}
lmod_length <- lm(Length ~ ., snails )
summary(lmod_length)
```

```{r}
lmod_width <- lm(Width ~ ., snails)
summary(lmod_width)
```

```{r}
lmod_AperHt <- lm(AperHt ~ ., snails )
summary(lmod_AperHt)
```

```{r}
lmod_AperWdt <- lm(AperWdt ~ ., snails)
summary(lmod_AperWdt)
```

```{r}
lmod_LU <- lm(LU ~ ., snails )
summary(lmod_LU)
```

```{r}
lmod_LipWdt <- lm(LipWdt ~ ., snails )
summary(lmod_LipWdt)
```